More than one Author with different Affiliations

### 2012-05-07 paper/ms.tex
Added idea about RJMCMC

>>>>

\subsection{Improving the Efficiency of Reversible Jump}
Instead of parameterising by $N$ and the positions and fluxes, what if we have
$3N_{\rm max}$ latent variables $\theta$ that always exist, and transform these
into
positions and fluxes by a transformation $f$:
\begin{eqnarray}
\{\mathbf{x}, \mathbf{y}, \mathbf{f}\} &=& f(\theta)
\end{eqnarray}
The transformation can be parameterised by various parameters of its own, such
that a known fraction of the fluxes end up being nonzero, etc. This could have
various advantages, most notably: when new stars are added, they are added with
low fluxes. It also turns the variable dimension problem into a fixed dimension
one, so emcee, MultiNest or similar will now work, although the multimodality problem will
still exist.
